---
output: 
  github_document:
    toc: TRUE

---



<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Objective 1: Introducing the {note} package! 

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->


The goal of {note} is to play notes using R, based in name (e.g. 'C'), duration of tone, and octave.

```
devtools::install_github("musician-tools/note")
```  
  
Try in an interactive session: 

```{r, eval = F}
library(note)
audio::play(note("A"))
```

# Objective 2. Immursive package building experience: readme as a checklist, control document 🚧 ✅ 


The package was initially conceived [by Jim Hester](https://resources.rstudio.com/rstudio-conf-2018/you-can-make-a-package-in-20-minutes-jim-hester){target="_blank"} as an example of how to quickly build an R package.  But this repo is also meant to be an *immursive* companion guide to Jim Hester's, 'You can make an R package in 20 minutes'.

I was extremely lucky to run across his talk when I did.  I had promised to write a package for an RConsortium grant, but I'm not sure that I would have managed without Jim's excellent walk-through. 

Recently I've explored 'literate package building' especially from the README, and have decided to return to Jim's package to further experiment with this idea - and because note deserves to be shared!

I've written a non-immursive companion guide to Jim's talk here: 
https://evamaerey.github.io/package_in_20_minutes/package_in_20_minutes


## Step 00: Press play *on the video guide*

Your video guide is [here](https://resources.rstudio.com/rstudio-conf-2018/you-can-make-a-package-in-20-minutes-jim-hester){target="_blank"}; the package build starts at about minute 8.   

# Part I. Work out functionality  ✅ 

Have some functions that you'd like to package up *like the below from Hester's 'note' example*

# helper objects and functions

```{r helperfunctions}
rate <- 44100
multiplier <- 2 * pi / rate
bpm <- 80
default_volume <- 5

note_names <- c("A" = 0, "A#" = 1, "Bb" = 1, "B" = 2, "Cb" = 2, "B#" = 3, "C" = 3,
  "C#" = 4, "Db" = 4, "D" = 5, "D#" = 6, "Eb" = 6, "E" = 7, "Fb" = 7, "E#" = 8,
  "F" = 8, "F#" = 9, "Gb" = 9, "G" = 10, "G#" = 11, "Ab" = 11)

rel3octaves <- stringr::str_split("DRMFSLTdrmfslt12345678", "")[[1]]
multiplier1octave <- c(1, 9/8, 81/64,4/3, 3/2, 27/16, 243/128)
mult3 <- c(multiplier1octave/2, multiplier1octave, multiplier1octave*2, 4)

drm_names <- mult3 
names(drm_names) <- rel3octaves

drm_to_freq <- function(drm = c("d", "r", "m"), freq_d = 440){
  
  drm_names[drm]*440
  
}

note_name_to_freq <- function(note_name, octave) {
  # 440hz is A above middle C
  440 * 2^((unname(note_names[note_name]) + (octave * 12)) / 12)
}

calc_volume <- function(x) {
  # x should be between 1 and 10
  stopifnot(x >= 1, x <= 10)
  
  x / 10
}

calc_duration <- function(rate, duration, bpm) {
  seq(1, as.integer(rate * duration * 60 / bpm))
}

calc_multiplier <- function(rate) {
  2 * pi / rate
}
```

# Exported 

## `note()`

```{r note}
#' note
#' 
#' @param name note name
#' @param octave octave
#' @param drm drm 
#' @param duration duration
#' @param volume volume
#'
#' @export
#'
#' @examples
#' note("A")
#' audio::play(c(
#' note("B", .5, 0),
#' note("E", .75, 0)))
note <- function(name = NULL, octave = 0, drm = NULL, duration = 1, volume = default_volume) {
  if(!is.null(name)){frequency <- note_name_to_freq(name, octave)}
  if(!is.null(drm)){frequency <- drm_to_freq(drm)}
  volume <- calc_volume(volume)
  duration <- calc_duration(rate, duration, bpm)
  multiplier <- calc_multiplier(rate)
  res <- sin(frequency * multiplier * duration) * volume
  structure(res, class = "note")
}


print.note_rel <- function(x, ...) {
  audio::play(x, ...)
}

print.note <- function(x, ...) {
  audio::play(x, ...)
}
```

## `potter_phrase_df`

```{r potter_phrase_df}
potter_phrase_df <- tibble::tribble(~note, ~duration, ~octave, 
         "B", .5, 0,
         "E", .75, 0,
         "G", .25, 0,
         "F#", .5, 0,
         "E", 1, 0,
         "B", .5, 1,
         "A", 1.5, 1,
         "F#", 1.5, 0) 

usethis::use_data(potter_phrase_df, overwrite = T)
```
## document_potter_phrase_df

```{r document_potter_phrase_df}
#' Harry Potter theme data frame
#'
#' Note, duration and  ...
#'
#' @format ## `potter_phrase_df`
#' A data frame with 8 rows:
#' \describe{
#'   \item{note}{note name}
#'   \item{duration}{duration of note}
#'   \item{octave}{note octave}
#'   ...
#' }
#' @source <https://www.warnerbros.com/movies/harry-potter-complete-8-film-collection>
"potter_phrase_df"



```
## `harry_potter_phrase_df`

```{r harry_potter_phrase_df}
twinkle_phrase_df <- tibble::tribble(~drm,~duration,
        "d", 1, 
         "d", 1, 
         "s", 1, 
         "s", 1, 
         "l", 1, 
         "l", 1, 
         "s", 2) 

usethis::use_data(twinkle_phrase_df, overwrite = T)
```

## document_twinkle_phrase_df

```{r document_twinkle_phrase_df}
#' Harry Potter theme data frame
#'
#' Note, duration and  ...
#'
#' @format ## `twinkle_phrase_df`
#' A data frame with 8 rows:
#' \describe{
#'   \item{drm}{note name using drm schema}
#'   \item{duration}{duration of note}
#'   ...
#' }
#' @source <https://www.warnerbros.com/movies/harry-potter-complete-8-film-collection>
"twinkle_phrase_df"



```


## `play_notes_df()` 

```{r play_notes_df}
#' play_notes_df
#'
#' @param data A data frame
#' @param name character variable with note names
#' @param octave numeric with note octave
#' @param duration numeric with note duration
#' @param volume numeric with note volume
#'
#' @return
#' @export
#'
#' @examples
play_notes_df <- function(data, name, octave, duration,  volume){
  
  rate <- 44100
  multiplier <- 2 * pi / rate
  bpm <- 80
  default_volume <- 5
  
  names = data |> dplyr::pull({{name}})
  durations = data |> dplyr::pull({{duration}})
  octaves = data |> dplyr::pull({{octave}})
  
  
  notes <- c()
    
    for (i in 1:nrow(data)){

    notes <- c(notes, 
               note(name = names[i],
                    octave = octaves[i],
                    duration = durations[i]
                            ))
        
    }
  
    audio::play(notes)

}
```

```{r}
potter_phrase_df |>
  play_notes_df(name = note, 
                duration = duration, 
                octave = octave)

```


## `play_drm_df()`


```{r play_drm_df}
#' play_drm_df
#'
#' @param data A data frame
#' @param drm a variable with drm encoding
#' @param duration note duration
#' @param volume volume duration
#'
#' @return will play notes
#' @export
#'
#' @examples  
play_drm_df <- function(data, drm, duration, volume){
  
  rate <- 44100
  multiplier <- 2 * pi / rate
  bpm <- 80
  default_volume <- 5
  

  drms = data |> dplyr::pull({{drm}}) 
  durations = data |> dplyr::pull({{duration}})
  volumes = data |> dplyr::pull({{volume}})
  
  
  notes <- c()
    
    for (i in 1:nrow(data)){

    notes <- c(notes, 
               note(drm = drms[i],
                    duration = durations[i]))
        
      }  
  
    
  audio::play(notes)
  
}
```

### Try this all out...

```{r}
twinkle_phrase_df |> 
  dplyr::mutate(volume = 1,
                duration = duration/2) |>
  play_drm_df(drm = drm, 
              duration = duration, 
              volume = volume)
```






## Phase 1. Minimal working package

```{r, eval = F}
# devtools::create(".")
```

### Added roxygen skeleton and manage dependancies? ✅ 

Use a roxygen skeleton for auto documentation and making sure proposed functions are *exported* and dependencies documented.

Package dependencies managed, i.e. `depend::function()` in proposed functions and declared in the DESCRIPTION

```{r}
usethis::use_package("audio")
usethis::use_package("dplyr")
```


### Moved functions R folder? ✅  

```{r}
knitrExtra::chunk_names_get()
knitrExtra::chunk_to_dir(c( "helperfunctions"   , "note"   , "potter_phrase_df","document_potter_phrase_df" , "harry_potter_phrase_df",       "document_twinkle_phrase_df"  , "play_notes_df", "play_drm_df"    ))
```


### Check and install

```{r, results='hide', error=T, eval = F}
devtools::document()
devtools::check(pkg = ".")
devtools::install(pkg = ".", upgrade = "never")
```



## Just beyond minimal

### Chosen a license? ✅ 


```{r}
usethis::use_mit_license()
usethis::use_lifecycle_badge("experimental")
```

## Phase 2: Listen & iterate 🚧 

Try to get feedback from experts on API, implementation, default decisions.  Is there already work that solves this problem? 


## Phase 3: Let things settle

- Settled on examples.  Put them in the roxygen skeleton and readme. 🚧 
- Written formal tests of functions? 🚧 


That would look like this...

```{r test_note_name_to_freq_works, eval = F}
library(testthat)

test_that("note_name_to_freq works", {
  expect_equal(note_name_to_freq("A", 0), 440)
  expect_equal(note_name_to_freq("A", -1), 220)
  
})
```

```{r}
knitrExtra:::chunk_to_tests_testthat("test_note_name_to_freq_works")
```

- add a description and author information in the DESCRIPTION file? 🚧 
- Addressed *all* notes, warnings and errors. 🚧 
- Promote to wider audience...
- Package website built? Package website deployed? Or don't. 🚧 
- Submit to CRAN? Or don't.  🚧 

```{r, eval = F}
# devtools::submit_cran()


```



