---
output: 
  github_document:
    toc: TRUE

---



<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Objective 1: Introducing the {note} package! 🦄 (typical package write up; but actually aspirational)

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->


The goal of {note} is to play notes using R, based in name (e.g. 'C'), length of tone, and octave.


```
devtools::install_github("musician-tools/note")
```  
  
## Example  🦄 (Aspirational; describes target API)

Try in an interactive session: 

```{r, eval = F}
library(note)
audio::play(note("A"))
```

# Objective 2. Immursive package building experience: readme as a checklist, control document 🚧 ✅ 


The package was initially conceived [by Jim Hester](https://resources.rstudio.com/rstudio-conf-2018/you-can-make-a-package-in-20-minutes-jim-hester){target="_blank"} as an example of how to quickly build an R package.  But this repo is also meant to be an *immursive* companion guide to Jim Hester's, 'You can make an R package in 20 minutes'.

I was extremely lucky to run across his talk when I did.  I had promised to write a package for an RConsortium grant, but I'm not sure that I would have managed without Jim's excellent walk-through. 

Recently I've explored 'literate package building' especially from the README, and have decided to return to Jim's package to further experiment with this idea - and because note deserves to be shared!

I've written a non-immursive companion guide to Jim's talk here: 
https://evamaerey.github.io/package_in_20_minutes/package_in_20_minutes


## Step 00: Press play *on the video guide*

Your video guide is [here](https://resources.rstudio.com/rstudio-conf-2018/you-can-make-a-package-in-20-minutes-jim-hester){target="_blank"}; the package build starts at about minute 8.   

# Part I. Work out functionality  ✅ 

Have some functions that you'd like to package up *like the below from Hester's 'note' example*

# helper objects and functions

```{r helperfunctions}
rate <- 44100
multiplier <- 2 * pi / rate
bpm <- 80
default_volume <- 5

note_names <- c("A" = 0, "A#" = 1, "Bb" = 1, "B" = 2, "Cb" = 2, "B#" = 3, "C" = 3,
  "C#" = 4, "Db" = 4, "D" = 5, "D#" = 6, "Eb" = 6, "E" = 7, "Fb" = 7, "E#" = 8,
  "F" = 8, "F#" = 9, "Gb" = 9, "G" = 10, "G#" = 11, "Ab" = 11)

rel3octaves <- stringr::str_split("DRMFSLTdrmfslt12345678", "")[[1]]
multiplier1octave <- c(1, 9/8, 81/64,4/3, 3/2, 27/16, 243/128)
mult3 <- c(multiplier1octave/2, multiplier1octave, multiplier1octave*2, 4)

drm_names <- mult3 
names(drm_names) <- rel3octaves

drm_to_freq <- function(drm = c("d", "r", "m"), freq_d = 440){
  
  drm_names[drm]*440
  
}

note_name_to_freq <- function(note_name, octave) {
  # 440hz is A above middle C
  440 * 2^((unname(note_names[note_name]) + (octave * 12)) / 12)
}

calc_volume <- function(x) {
  # x should be between 1 and 10
  stopifnot(x >= 1, x <= 10)
  
  x / 10
}

calc_length <- function(rate, length, bpm) {
  seq(1, as.integer(rate * length * 60 / bpm))
}

calc_multiplier <- function(rate) {
  2 * pi / rate
}
```

# Exported 

## `note()`

```{r note}
#' @export
#'
#' @examples
#' note("A")
#' audio::play(c(
#' note("B", .5, 0),
#' note("E", .75, 0)))
note <- function(note_name = NULL, drm = NULL, length = 1, octave = 0, volume = default_volume) {
  if(!is.null(note_name)){frequency <- note_name_to_freq(note_name, octave)}
  if(!is.null(drm)){frequency <- drm_to_freq(drm)}
  volume <- calc_volume(volume)
  length <- calc_length(rate, length, bpm)
  multiplier <- calc_multiplier(rate)
  res <- sin(frequency * multiplier * length) * volume
  structure(res, class = "note")
}

# note(drm = "d", volume = 5)


# audio::play(note_rel(doremi = "8"))


print.note_rel <- function(x, ...) {
  audio::play(x, ...)
}

print.note <- function(x, ...) {
  audio::play(x, ...)
}
```


## `play_notes_df()`

```{r }
harry_potter_phrase_df <- tibble::tribble(~name,~length,~octave, 
        "B", .5, 0,
         "E", .75, 0,
         "G", .25, 0,
         "F#", .5, 0,
         "E", 1, 0,
         "B", .5, 1,
         "A", 1.5, 1,
         "F#", 1.5, 0) 
```



```{r play_notes_df}
#' Title
#'
#' @param df 
#' @param name 
#' @param length 
#' @param octave 
#' @param volume 
#'
#' @return
#' @export
#'
#' @examples
play_notes_df <- function(df, note_name, length, octave, volume){
  
  rate <- 44100
  multiplier <- 2 * pi / rate
  bpm <- 80
  default_volume <- 5
  
  note_names = df |> dplyr::pull({{note_name}})
  lengths = df |> dplyr::pull({{length}})
  octaves = df |> dplyr::pull({{octave}})
  
  
  notes <- c()
    
    for (i in 1:nrow(df)){

    notes <- c(notes, 
               note(note_name = note_names[i],
                    length = lengths[i],
                    octave = octaves[i]
                            ))
        
    }
  
    audio::play(notes)

}
  
  
play_drm_df <- function(df, drm, length, volume){
  
  rate <- 44100
  multiplier <- 2 * pi / rate
  bpm <- 80
  default_volume <- 5
  

  drms = df |> dplyr::pull({{drm}}) 
  lengths = df |> dplyr::pull({{length}})
  volumes = df |> dplyr::pull({{volume}})
  
  
  notes <- c()
    
    for (i in 1:nrow(df)){

    notes <- c(notes, 
               note(note_name = note_names[i],
                    drm = drms[i],
                    length = lengths[i]))
        
      }  
  
    
  audio::play(notes)
  
}
```


```{r}
harry_potter_phrase_df |>
  play_notes_df(note_name = name, 
                length = length, 
                octave = octave)

library(tidyverse)
ggdoremi:::parse_phrases_drm("ddssllssffmmrrdd", base_freq = 440) |>
  dplyr::mutate(length = 1, volume = 2) |>
  play_drm_df(drm = drm, length = length, volume = volume)

ggdoremi:::parse_phrases_drm("mssssllt
                             t1111112
                             2222233322") |>
  ungroup() |>
  dplyr::mutate(length = rep(c(1,2), 13)/1.4,
         volume = 1) |> 
  play_drm_df(drm = drm, length = length, volume = volume)


```






## Phase 1. Minimal working package

```{r, eval = F}
# devtools::create(".")
```

### Added roxygen skeleton and manage dependancies? ✅ 

Use a roxygen skeleton for auto documentation and making sure proposed functions are *exported* and dependencies documented.

Package dependencies managed, i.e. `depend::function()` in proposed functions and declared in the DESCRIPTION

```{r}
usethis::use_package("audio")
```


### Moved functions R folder? ✅  

```{r}
knitrExtra::chunk_names_get()
knitrExtra::chunk_to_dir(c("helperfunctions", "note", "play_notes_df"))
```

### Package data set

```{r harry_potter_phrase_df}
harry_potter_phrase_df <- tibble::tribble(~name,~length,~octave, 
        "B", .5, 0,
         "E", .75, 0,
         "G", .25, 0,
         "F#", .5, 0,
         "E", 1, 0,
         "B", .5, 1,
         "A", 1.5, 1,
         "F#", 1.5, 0) 

usethis::use_data(harry_potter_phrase_df, overwrite = T)
```



```{r}
# usethis::use_data_raw()
knitrExtra::chunk_to_dir(c("harry_potter_phrase_df"), 
                         dir = "data-raw")
```

### Check and install

```{r, results='hide', error=T, eval = F}
devtools::check(pkg = ".")
devtools::install(pkg = ".", upgrade = "never")
```

### Traditional readme

```{r, eval = F}
# library(note)

audio::play(note("A"))

audio::play(c(
note("B", .5, 0),
note("E", .75, 0),
note("G", .25, 0)
))

harry_potter_phrase_df |>
  play_notes_df(name = name, 
                length = length, 
                octave = octave)


```




## Just beyond minimal

### Chosen a license? ✅ 


```{r}
usethis::use_mit_license()
usethis::use_lifecycle_badge("experimental")
```

## Phase 2: Listen & iterate 🚧 

Try to get feedback from experts on API, implementation, default decisions.  Is there already work that solves this problem? 


## Phase 3: Let things settle

- Settled on examples.  Put them in the roxygen skeleton and readme. 🚧 
- Written formal tests of functions? 🚧 


That would look like this...

```{r test_calc_frequency_works, eval = F}
library(testthat)

test_that("calc frequency works", {
  expect_equal(calc_frequency("A", 0), 440)
  expect_equal(calc_frequency("A", -1), 220)
  
})
```

```{r}
knitrExtra:::chunk_to_tests_testthat("test_calc_frequency_works")
```

- add a description and author information in the DESCRIPTION file? 🚧 
- Addressed *all* notes, warnings and errors. 🚧 
- Promote to wider audience...
- Package website built? 🚧 
- Package website deployed? 🚧 
- Submit to CRAN? Or don't.  🚧 





