---
output: 
  github_document:
    toc: TRUE

---



<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Objective 1: Introducing the {note} package! 🦄 (typical package write up; but actually aspirational)

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->


The goal of {note} is to play notes using R, based in name (e.g. 'C'), length of tone, and octave.


```
devtools::install_github("musician-tools/note")
```  
  
## Example  🦄 (Aspirational; describes target API)

Try in an interactive session: 

```{r, eval = F}
library(note)
audio::play(note("A"))
```

# Objective 2. Immursive package building experience: readme as a checklist, control document 🚧 ✅ 


The package was initially conceived [by Jim Hester](https://resources.rstudio.com/rstudio-conf-2018/you-can-make-a-package-in-20-minutes-jim-hester){target="_blank"} as an example of how to quickly build an R package.  But this repo is also meant to be an *immursive* companion guide to Jim Hester's, 'You can make an R package in 20 minutes'.

I was extremely lucky to run across his talk when I did.  I had promised to write a package for an RConsortium grant, but I'm not sure that I would have managed without Jim's excellent walk-through. 

Recently I've explored 'literate package building' especially from the README, and have decided to return to Jim's package to further experiment with this idea - and because note deserves to be shared!

I've written a non-immursive companion guide to Jim's talk here: 
https://evamaerey.github.io/package_in_20_minutes/package_in_20_minutes


## Step 00: Press play *on the video guide*

Your video guide is [here](https://resources.rstudio.com/rstudio-conf-2018/you-can-make-a-package-in-20-minutes-jim-hester){target="_blank"}; the package build starts at about minute 8.   

# Part I. Work out functionality  ✅ 

Have some functions that you'd like to package up *like the below from Hester's 'note' example*


```{r hesterfunctions}
rate <- 44100
multiplier <- 2 * pi / rate
bpm <- 80
default_volume <- 5

notes <- c("A" = 0, "A#" = 1, "Bb" = 1, "B" = 2, "Cb" = 2, "B#" = 3, "C" = 3,
  "C#" = 4, "Db" = 4, "D" = 5, "D#" = 6, "Eb" = 6, "E" = 7, "Fb" = 7, "E#" = 8,
  "F" = 8, "F#" = 9, "Gb" = 9, "G" = 10, "G#" = 11, "Ab" = 11)

calc_frequency <- function(note, octave) {
  # 440hz is A above middle C
  440 * 2^((unname(notes[note]) + (octave * 12)) / 12)
}

calc_volume <- function(x) {
  # x should be between 1 and 10
  stopifnot(x >= 1, x <= 10)
  
  x / 10
}

calc_length <- function(rate, length, bpm) {
  seq(1, as.integer(rate * length * 60 / bpm))
}

calc_multiplier <- function(rate) {
  2 * pi / rate
}

#' Create music
#'
#' @param note name
#' @param length in beats
#' @param octave from middle C
#' @param volume from 1 to 10
#'
#' @return a note object
#' @export
#'
#' @examples
#' note("A")
#' audio::play(c(
#' note("B", .5, 0),
#' note("E", .75, 0),
#' note("G", .25, 0),
#' note("F#", .5, 0),
#' note("E", 1, 0),
#' note("B", .5, 1),
#' note("A", 1.5, 1),
#' note("F#", 1.5, 0)
#' ))
note <- function(name, length = 1, octave = 0, volume = default_volume) {
  frequency <- calc_frequency(name, octave)
  volume <- calc_volume(volume)
  length <- calc_length(rate, length, bpm)
  multiplier <- calc_multiplier(rate)
  res <- sin(frequency * multiplier * length) * volume
  structure(res, class = "note")
}

rel3octaves <- stringr::str_split("DRMFSLTdrmfslt12345678", "")[[1]]
multiplier1octave <- c(1, 9/8, 81/64,4/3, 3/2, 27/16, 243/128)
mult3 <- c(multiplier1octave/2, multiplier1octave, multiplier1octave*2, 4)


calc_freq_relative <- function(doremi = "d", 
                               do_freq = 440 #A above middle C
                               ){
  
  440*mult3[which(rel3octaves == doremi)]
  
}

calc_freq_relative()

note_rel <- function(doremi, do_freq = 440, length = 1, volume = default_volume) {
  
  frequency <- calc_freq_relative(doremi, do_freq)
  volume <- calc_volume(volume)
  length <- calc_length(rate, length, bpm)
  multiplier <- calc_multiplier(rate)
  res <- sin(frequency * multiplier * length) * volume
  structure(res, class = "note")
  
}


# audio::play(note_rel(doremi = "8"))


print.note_rel <- function(x, ...) {
  audio::play(x, ...)
}

print.note <- function(x, ...) {
  audio::play(x, ...)
}

#' Title
#'
#' @param df 
#' @param name 
#' @param length 
#' @param octave 
#' @param volume 
#'
#' @return
#' @export
#'
#' @examples
play_notes_df <- function(df, name, length, octave, volume){
  
  rate <- 44100
  multiplier <- 2 * pi / rate
  bpm <- 80
  default_volume <- 5
  
  notes <- c()
    
    for (i in 1:nrow(df)){

    notes <- c(notes, note(name = df %>% pull({{name}}) %>% .[i],
       length = (df %>% pull({{length}}) %>% .[i]),
       octave = df %>% pull({{octave}}) %>% .[i]
                            ))
        
      }
    
  audio::play(notes)
  
  }
    


note_movable <- function(){
  

  
}
  
  


```





# Part II. Packaging and documentation  🚧 ✅ 



## Phase 1. Minimal working package

### Created files for package archetecture with `devtools::create(".")` ✅ 

### Moved functions R folder? ✅  

```{r}
knitr::knit_code$get() |> names()
```

Use new {readme2pkg} function to do this from readme...

```{r, eval = F}
readme2pkg::chunk_to_r("hesterfunctions")
```



### Added roxygen skeleton? ✅ 

Use a roxygen skeleton for auto documentation and making sure proposed functions are *exported*.

### Managed dependencies ? ✅ 

Package dependencies managed, i.e. `depend::function()` in proposed functions and declared in the DESCRIPTION

```{r}
usethis::use_package("audio")
```



### Chosen a license? ✅ 


```{r}
usethis::use_mit_license()
```

### Run `devtools::check()` and addressed errors? ✅ 

```{r, results='hide', error=T}
devtools::check(pkg = ".")
```

### Build package 🚧 

```{r}
devtools::build()
```

You need to do this before library(mynewpackage) will work.

### Make aspirational part of readme real. 🚧 

At this point, you could change eval chunk options to TRUE. You can remove  the 🦄 emoji and perhaps replace it with construction site if you are still uncertain of the API, and want to highlight that it is subject to change. 

### Add lifecycle badge (experimental)

```{r}
usethis::use_lifecycle_badge("experimental")
```


## Phase 2: Listen & iterate 🚧 

Try to get feedback from experts on API, implementation, default decisions.  Is there already work that solves this problem? 


## Phase 3: Let thinggs settle

### Settled on examples.  Put them in the roxygen skeleton and readme. 🚧 

### Written formal tests of functions? 🚧 


That would look like this...

```{r test_calc_frequency_works}
library(testthat)

test_that("calc frequency works", {
  expect_equal(calc_frequency("A", 0), 440)
  expect_equal(calc_frequency("A", -1), 220)
  
})
```


```{r}
readme2pkg::chunk_to_tests_testthat("test_calc_frequency_works")
```


### Have you worked added a description and author information in the DESCRIPTION file? 🚧 

### Addressed *all* notes, warnings and errors. 🚧 

## Promote to wider audience...

### Package website built? 🚧 

### Package website deployed? 🚧 

## Phase 3: Harden/commit

### Submit to CRAN? Or don't.  🚧 

# Appendix: Reports, Environment

## Description file extract

```{r}

```

## Environment

Here I just want to print the packages and the versions

```{r}
all <- sessionInfo() |> print() |> capture.output()
all[11:17]
```

## `devtools::check()` report

```{r, error = T, results="hide", warning=F}
devtools::check(pkg = ".")
```




